---
title: "Clean transcripts"
author: "Nathaniel Olin"
date: "`r date()`"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(tidyverse)
```

# Load data

## Metadata

```{r load-meta}
dat <- read_csv("meta.csv")
# Remove locked transcript
# dat <- dat %>%
#   filter(filename != "2.0_06_heres_your_bribe_tip.txt")
```

## Transcripts

```{r load-transcripts, warning = F}
dat <- dat %>%
  filter(complete) %>%
  mutate(
    filename = file.path("transcripts", filename),
    raw_text = sapply(
      filename,
      readLines, encoding = "UTF-8")
  )

dat %>%
  filter(season_id == 4 & episode_id == 1) %>%
  select(raw_text) %>%
  unlist() %>%
  .[100:120] %>%
  .[. != ""] %>%
  paste(collapse = "\n") %>%
  writeLines()
```

# Clean transcripts

Split text into groups: 

1. Whitespace
1. Text until colon
1. All following characters

```{r}
split_pattern <- "^ *(.+?): *(.*)"
```

Turn raw text vector into dataframe with speaker, text, and raw (original text) columns

```{r}
dat <- dat %>%
  mutate(text = lapply(
    raw_text, function(x){
      x <- str_replace(x, "^$", "\n")
      x <- paste(x, collapse = "")
      x <- unlist(strsplit(x, "\n"))
      tibble(
        line = 1:length(x),
        speaker = toupper(str_replace_all(x, split_pattern, "\\1")),
        text = str_replace_all(x, split_pattern, "\\2"),
        raw = x) %>%
        # Remove lines with blank speaker and blank text
        filter(! (speaker %in% c("", " ") & text %in% c("", " "))) %>%
        # filter(! str_detect(speaker, "^ *\\[")) %>%
        mutate(speaker = if_else(text == raw, as.character(NA), speaker))
    }))
```

Collapse text dataframes

```{r}
dat_line <- bind_rows(dat$text, .id = "filename") %>%
  # Remove rows without speaker / text
  filter(speaker != toupper(raw)) %>%
  # Remove timestamps
  filter(! str_detect(raw, "[0-9]: *[0-9]{2}[:.][0-9]{2}")) %>%
  filter(! str_detect(raw, "[0-9]+:[0-9]{2}")) %>%
  filter(! str_detect(raw, "TIMESTAMP")) %>%
  # Remove blank rows
  filter(! str_detect(raw, "^ *$"))
```

Remove "(...): " pattern which indicates who the speaker is impersonating

```{r}
dat_line <- dat_line %>%
  mutate(speaker = str_remove(speaker, " +\\(.*\\)| +\\[.*\\]"))
```


## Real speakers

```{r}
fix_name <- function(col, x) str_detect(col, x) ~ x
dat_line <- dat_line %>%
  mutate(speaker = case_when(
    fix_name(speaker, "AUSTIN"),
    fix_name(speaker, "KEITH"),
    fix_name(speaker, "JACK"),
    fix_name(speaker, "ALI"),
    fix_name(speaker, "ART"),
    fix_name(speaker, "DRE"),
    fix_name(speaker, "JANINE"),
    fix_name(speaker, "SYLVIA"), 
    fix_name(speaker, "NICK"),
    TRUE ~ speaker
  ))
```

```{r}
recode_speaker <- function(d, player, alias) {
  alias <- paste(alias, collapse = "|")
  d %>%
    mutate(speaker = if_else(
      str_detect(speaker, alias), 
      player, 
      speaker
    ))
}
```

```{r recode-characters}
dat_line <- dat_line %>%
  recode_speaker("KEITH", c("FERO", "MAKO", "GIG")) %>%
  mutate(speaker = if_else(
    speaker %in% c("KIETH", "KETH", "KETIH", "KETIH", "KEI"),
    "KEITH", speaker)) %>%
  recode_speaker("JACK", c(
    "LEM", "AUDY", "HITCHCOCK", "ETHAN", 
    "EDMUND", "FOURTEEN")) %>%
  mutate(speaker = if_else(
    speaker %in% c("JAC", "JAKC", "JAKE", "JCK"),
    "JACK", speaker)) %>%
  recode_speaker("ALI", c("HELLA", "ARIA", "CASTILLE", "TENDER", "BROUN")) %>%
  mutate(speaker = if_else(
    speaker %in% c("ADI", "AII", "AL", "ARI"),
    "ALI", speaker)) %>%
  recode_speaker("DRE", c("THRONDIR", "SIGE", "EVEN", "VALENCE")) %>%
  mutate(speaker = if_else(speaker %in% c("DE"), "DRE", speaker)) %>%
  recode_speaker("SYLVIA", c("AUBREY", "EPHRIM", "ECHO", "SYLVI", "SYLIVA")) %>%
  mutate(speaker = if_else(
    speaker %in% c("ANSDI", "SILVIA", "SYLVA", "SYVIA"), 
    "SYLVIA", speaker)) %>%
  recode_speaker("JANINE", c("ADAIRE", "SIGNET", "THISBE")) %>%
  mutate(speaker = if_else(speaker %in% c("JAININE"), "JANINE", speaker)) %>%
  recode_speaker("NICK", c("PHANTASMO", "FANTASMO")) %>%
  recode_speaker("ART", c("HADRIAN", "CASS")) %>%
  mutate(speaker = if_else(speaker %in% c("T", "ASRT", "RT"), "ART", speaker))
```

```{r recode-austin}
# recode exact:
dat_line <- dat_line %>%
  mutate(speaker = if_else(
    speaker %in% c(
      "A", "AU", "AUS", "AUS.", "AUSIN", "AUTIN", "AUDTIN", 
      "AUD", "AUSINT", "AUSITN", "AUST", "AUSTI"), 
    "AUSTIN", 
    speaker))
# recode str_detect
dat_line <- dat_line %>%
  recode_speaker("AUSTIN", c(
    "SAMOL",
    "SAMOT",
    "BLUE J",
    "SEVEREA",
    "TED",
    "CASCARA",
    "ARRELL",
    "CARLAY", 
    "MAELGWYN",
    "PRIMO",
    "RIX",
    "ARIN TILL",
    "JAZELLA",
    "SNITCH",
    "SAMOTHES",
    "MARYLAND",
    "MAXINE",
    "MARITIME",
    "UKLAN",
    "PRETENSE",
    "REBECCA",
    "LENNY",
    "VULTURE",
    "GALENICA",
    "BURGLAR",
    "FAUL",
    "TOWER",
    "BENJAMIN",
    "CELADOR",
    "CALLER",
    "CORAL",
    "CADENT",
    "FENTIL",
    "ISAAC",
    "MAN",
    "TAVIRA",
    "CORSICA",
    "HEDY",
    "SILAS",
    "LARDWULF",
    "SOL",
    "URRN",
    "BLAKE",
    "IRIS",
    "PEG",
    "AVORA",
    "ADELTON",
    "HIGHWATER",
    "ALYOSHA",
    "SOL",
    "GLORY",
    "SAM",
    "WES",
    "WYNTER",
    "FENOLO",
    "JESSET",
    "DUKE",
    "INVESTIGATOR",
    "COREY",
    "ORTH",
    "ROSANA",
    "THE GIRL",
    "WEAVER",
    "BIRDS",
    "ADDAX",
    "KODIAK",
    "PORTO PORLO PINTA",
    "ROE",
    "SHO",
    "SOMEONE",
    "AVAR",
    "INN-KEEPER",
    "CALHOUN",
    "SPRINGE",
    "ORDENNAN",
    "ADLETON",
    "BEN",
    "ICE LADY",
    "JAMIL",
    "KALL",
    "MORBASH",
    "OPENING NARRATION",
    "ORCHID",
    "SMOLDER",
    "THE KILLER",
    "THE OGRE",
    "ZAHN",
    "ALEJANDRO",
    "BLOOMING",
    "ZHAN",
    "MEE KOSH",
    "OORN",
    "RANDOM PERSON",
    "RAPHOA",
    "RYRIRA",
    "SABEEHA",
    "\\[SLIDE",
    "ADELAIDE",
    "GRAY",
    "MOTION",
    "RECEPTIONIST",
    "RETAIL DRONE",
    "RODENTS",
    "SKELETON", # RIP
    "UNNAMED TROOP PILOT",
    "CHRISTOPHER",
    "ELF",
    "FESTER",
    "JACQUI",
    "MAYLAND",
    "MOURNING BRIDE",
    "SUNDER",
    "THE PRINCEPT",
    "ZEALOT SAYS",
    "A LETTER FROM KENT BRIGHTON TO THE LINEAGE’S MATRIARCH, THE LADY LYME",
    "AND ALL OF THIS IS WHY I HATE THAT OLD DEBATE",
    "YOU HAVE SERVED ME WELL YET AGAIN, GRAND MARSHAL. YET I SENSE IN YOU SOMETHING SHAMEFUL"
  ))
```

Remove non-players

```{r}
dat_line <- dat_line %>%
  filter(! str_detect(speaker, "\\[*MUSIC")) %>%
  filter(! str_detect(
    speaker, 
    "HIERON|HEIRON|MARIELDA|TWILIGHT MIRAGE|COUNTER/WEIGHT|PARTIZAN|LIVE AT THE TABLE|TRANSCR")) %>%
  filter(! speaker %in% c(
    "__",
    "[T/N",
    "* NOTE",
    "[A]NOTE FOR NEW LISTENERS",
    "[A WHIRLWIND OF INSTRUCTIONS FROM EVERYONE ABOUT HOW THIS WORKS, INCLUDING",
    "ALL",
    "EVERYONE",
    "[EVERYONE MAKES NOISES OF UNDERSTANDING, EG",
    "[INTRO THEME",
    "[BACKGROUND NOISE",
    "(OVERLAPPED)",
    "(OVERLAPPING)",
    "??? ",
    "[???]",
    "[EVERYONE MAKES SURPRISED NOISES. EG",
    "[UNKNOWN]",
    "CW",
    "________________[1] FELAN PARKER HTTPS",
    "“TELL ME” LYRICS",
    "FEATURING",
    "PLEASE NOTE",
    "ROBOT",
    "ROBOT SYNTHESIZER VOICE",
    "ROBOT VOICE",
    "SEVERAL PEOPLE",
    "SEVERAL PEOPLE IN UNISON"
  ))
```


Remaining lines coded as speaker above

```{r}
# Confirm all first-line speakers are valid
valid_speaker <- dat_line %>%
  count(speaker) %>%
  filter(n > 100) %>%
  select(speaker) %>%
  unlist()

dat_line <- dat_line %>% 
  group_by(filename) %>% 
  mutate(first_line = line == min(line)) %>%
  ungroup()

dat_line %>% filter(first_line) %>% count(speaker)
stopifnot(dat_line$speaker[dat_line$first_line] %in% valid_speaker)

# Remove invalid
dat_line$speaker[! dat_line$speaker %in% valid_speaker] <- NA
  
while(! all(dat_line$speaker %in% valid_speaker)){
  # Replace with line above
  invalid <- is.na(dat_line$speaker)
  dat_line$speaker[invalid] <- dat_line$speaker[which(invalid) - 1]
}
dat_line %>% count(speaker)
rm(invalid)
```

# Write out

```{r}
dat_line %>%
  print() %>%
  write_csv("line.csv")
```


