---
title: "Clean transcripts"
author: "Nathaniel Olin"
date: "`r date()`"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(tidyverse)
```

# Load data

## Metadata

```{r load-meta}
dat <- read_csv("meta.csv")
# Remove locked transcript
dat <- dat %>%
  filter(filename != "2.0_06_heres_your_bribe_tip.txt")
```

## Transcripts

```{r load-transcripts, warning = F}
dat <- dat %>%
  mutate(
    filename = file.path("transcripts", filename),
    raw_text = sapply(
      filename,
      readLines, encoding = "UTF-8"))

dat %>%
  filter(season_number == 4 & episode_number == 1) %>%
  select(raw_text) %>%
  unlist() %>%
  .[100:120] %>%
  paste(collapse = "\n") %>%
  writeLines()
```

# Clean transcripts

Split text into groups: 

1. whitespace or leading punctuation
1. Text until new punctuation or space
1. New punctuation or space and all following characters

```{r}
split_pattern <- "^[ *().]*(.+?)[!?,: /\\[\\]().;—-]+(.*)"
```

Turn raw text vector into dataframe with speaker, text, and raw (original text) columns

```{r}
dat <- dat %>%
  mutate(text = lapply(
    raw_text, function(x){
      tibble(line = 1:length(x),
             speaker = toupper(str_replace_all(x, split_pattern, "\\1")),
             text = str_replace_all(x, split_pattern, "\\2"),
             raw = x) %>%
        filter(! (speaker %in% c("", " ") & text %in% c("", " "))) %>%
        filter(! str_detect(speaker, "^ *\\[")) %>%
        mutate(speaker = if_else(text == raw, as.character(NA), speaker))
    }))
```

Collapse text dataframes

```{r}
dat_line <- bind_rows(dat$text, .id = "filename") %>%
  # Remove rows without speaker / text
  filter(speaker != toupper(raw)) %>%
  # Remove timestamps
  filter(! str_detect(raw, "^\\(*[0-9]: *[0-9]{2}[:.][0-9]{2}\\)*")) %>%
  # Remove blank rows
  filter(! str_detect(raw, "^ *$"))
```

## Real speakers

```{r}
speaker_recode <- list(
  AUSTIN = c(
    "SAMOL",
    "SAMOT",
    "SEVEREA",
    "TED",
    "ARRELL",
    "MAELGWYN",
    "PRIMO",
    "RIX",
    "MARYLAND",
    "SNITCH",
    "JAZELLA",
    "SAMOTHES",
    "MAXINE",
    "MARITIME",
    "UKLAN",
    "EDMUND",
    "REBECCA",
    "VULTURE",
    "GALENICA",
    "TOWER",
    "BENJAMIN",
    "CELADOR",
    "CALLER",
    "CORAL",
    "CASCARA",
    "FENTIL",
    "AUS",
    "CORSICA",
    "HEDY",
    "SILAS",
    "URRN",
    "IRIS",
    "PEG",
    "ADELTON",
    "HIGHWATER",
    "JACQUI",
    "ORCHID",
    "AL",
    "EMMANUEL",
    "SAM",
    "ADDAX",
    "ORTH",
    "ROSANA",
    "WEAVER",
    "ARR",
    "CENE",
    "DEMANI",
    "KODIAK",
    "ROE",
    "ADLETON",
    "BALION",
    "BEN",
    "CLANK",
    "CRYSTAL",
    "ECHO",
    "IBEX",
    "ICE",
    "JAMIL",
    "KALL",
    "MORBASH",
    "OORN",
    "RED",
    "VOLITION",
    "ZHAN",
    "JULIA",
    "ABDICATOR",
    "ALEXIS",
    "ASTIN",
    "AUST",
    "AUSITN",
    "AUSTI",
    "AUSTINS",
    "AUSTN",
    "AUTIN",
    "AXIOMS",
    "BALLAD",
    "BLACKFORD",
    "BLAKE",
    "BLUEBERRI",
    "BRIGHTON",
    "CAPTAIN",
    "CHORUS",
    "CHRISTOPHER",
    "CLARINENTS",
    "CLARINETS",
    "CODA",
    "CORRECTIVE",
    "COWBOY",
    "CURIOSITY",
    "DETACHMENT",
    "ELGASH",
    "INDIANA",
    "LIBERTY",
    "LULAV",
    "MASSALIA",
    "MAYLAND",
    "MOONLOCK",
    "NATALIA",
    "NATALYA",
    "OBELDAY",
    "PRIMARY",
    "SENESCHAL'S",
    "STORNRAS",
    "TAMSIN",
    "TANNER",
    "THYRSUS",
    "KATIE",
    "JERRY",
    "WALTZ",
    "KADAKNATH",
    "KADAKNATH'S",
    "JORNE",
    "JORAS",
    "KARAS",
    "SMOLDER",
    "SUNDER",
    "SHO",
    "AMAYA",
    # Hitchcock's friend = snitch nightly
    "HITCHCOCK’S",
    "AU",
    "BLUE"
  ),
  KEITH = c(
    "FERO", 
    "MAKO",
    "GIG",
    "KETH",
    "KEI",
    "KETIH"
  ),
  JACK = c(
    "HITCHCOCK",
    "LEM",
    "AUDY",
    "ETHAN",
    "LEMME",
    "AUD",
    "FOURTEEN",
    "JACKK",
    "JACK’S"
  ),
  ALI = c(
    "HELA",
    "HELLA",
    "CASTILLE",
    "ARIA",
    "TENDER",
    "ALII",
    "ALIS",
    "ARIANA"
  ),
  ART = c(
    "HADRIAN",
    "CASS",
    "GRAND"
  ),
  ANDI = c(
    "EPHRIM",
    "AUBREY",
    "ANDJ",
    "ANID",
    "JANDI",
    "ANSDI"
  ),
  DRE = c(
    "ANDREW",
    "THRONDIR",
    "SIGE",
    "DERL"
  ),
  JANINE = c(
    "ADAIRE",
    "SIGNET",
    "JANIN",
    "JAINE"
  ),
  NICK = c(),
  TRANSCRIBER = c(
    "TRANSCRIPTION",
    "TRANSCRIBER’S",
    "TRANSCRIBERS"
  )
)
```

Recode speakers

```{r}
for(i in seq_along(speaker_recode)){
  dat_line$speaker[dat_line$speaker %in% speaker_recode[[i]]] <- names(speaker_recode)[i]
}

dat_line %>%
  count(speaker, sort = T) %>%
  select(speaker) %>%
  unlist() %>% unname()
```

Remaining lines coded as speaker above

```{r}
dat_line$speaker[dat_line$line == 1] <- NA
for(i in seq_along(dat_line$speaker)){
  # If you're not on the list of "real" speakers
  if(! dat_line$speaker[i] %in% names(speaker_recode) & dat_line$line[i] > 1){
    # You're a carryover from the line above, and
    dat_line$speaker[i] <- dat_line$speaker[i - 1]
    # Your text should stay as written
    dat_line$text[i] <- dat_line$raw[i]
  }
}

dat_line %>% count(speaker)
```

# Write out

```{r}
dat_line %>%
  print() %>%
  write_csv("line.csv")
```


